Balance responses in MS

### 2020-01-28 R/msBalance.Rmd
added processing code to time-align emg and kinematic signals. discovered some significant issues with kinematic marker dropout, sent query to dan about perturbationOnset data.

## Data processing
Each individual EMG record was registered to the onset of treadmill motion and resampled to a common timebase.

```{r}
# if trial-level data files do not exist, run matlab batch steps to populate them
if (!file.exists("../tmp/Treadmill.csv")){
  system(paste(matlabCommand, "'cd ../m; preprocessData; exit'"))
}
```

>>>>

## Data processing
Each individual EMG record was registered to the onset of treadmill motion and resampled to a common sample rate (1 kHz), and processed (high-pass, 35 Hz, de- mean, rectify, low-pass, 40 Hz) as in previous studies.[@lang2019; @mckay2016]

```{r}
# if trial-level data files do not exist, run matlab batch steps to populate them
if (!file.exists("../tmp/Participant.csv")|
    !file.exists("../tmp/Date.csv")|
    !file.exists("../tmp/Trial.csv")|
    !file.exists("../tmp/Time.csv")|
    !file.exists("../tmp/Treadmill.csv")|
    !file.exists("../tmp/Emg1.csv")|
    !file.exists("../tmp/Emg2.csv")|
    !file.exists("../tmp/Emg3.csv")|
    !file.exists("../tmp/Emg4.csv")){
  system(paste(matlabCommand, "'cd ../m; preprocessData; exit'"))
}
trialData = cbind(
vroom("../tmp/Participant.csv", col_names = FALSE) %>% select(Participant = X1),
vroom("../tmp/Date.csv", col_names = FALSE) %>% select(Date = X1),
vroom("../tmp/Trial.csv", col_names = FALSE) %>% select(Trial = X1)
) %>% as_tibble() %>% mutate(Date = ymd(Date))

time = vroom("../tmp/Time.csv", col_names = FALSE)
treadmill = vroom("../tmp/Treadmill.csv", col_names = FALSE)
emg1 = vroom("../tmp/Emg1.csv", col_names = FALSE)
emg2 = vroom("../tmp/Emg2.csv", col_names = FALSE)
emg3 = vroom("../tmp/Emg3.csv", col_names = FALSE)
emg4 = vroom("../tmp/Emg4.csv", col_names = FALSE)

```
